---
title: "Create_SeeGEM_report"
author: "David McGaughey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

I imagine most users of [GEMINI](http://gemini.readthedocs.io) have built fairly
complicated sets of queries to handle their needs. [GEMINI](http://gemini.readthedocs.io) 
provides a large set of 
[built in tools](http://gemini.readthedocs.io/en/latest/content/tools.html#autosomal-dominant-find-variants-meeting-an-autosomal-dominant-model)
as well as a very powerful SQL-based custom [query builder](http://gemini.readthedocs.io/en/latest/content/querying.html).

For each of our exomes and WGS, we use many of the built in [GEMINI](http://gemini.readthedocs.io)
tools as well as a custom query to identify deleterious variants in the 
[ACMG 59 gene list](https://www.ncbi.nlm.nih.gov/clinvar/docs/acmg/). 

In the [Quick Start](Quick_Start.Rmd) vignette we see how SeeGEM can be used to
quickly and easily create the SeeGEM document for a single query. 

In this vignette we will see how to bundle together a complicated set of queries
and a [peddy](https://www.ncbi.nlm.nih.gov/clinvar/docs/acmg/) quality control
output into a SeeGEM document. 

Most importantly, this approach is fully scriptable and can be easily fit into
a pipeline. 

A working script that makes a large set of [GEMINI](http://gemini.readthedocs.io)
queries and creates SeeGEM output is included in this package. It can be copied
to your home directory as follows:

```{r, eval=F}
system(paste('cp', 
             system.file("example_scripts/GEMINI_db_to_SeeGEM.R", package="SeeGEM"), 
             '~/GEMINI_db_to_SeeGEM.R'))
```

It takes four inputs:

1. The path to the GEMINI database
2. The name of the family (from the ped file) to be analyzed
3. The path and name of your output SeeGEM html file
4. The path and prefix of your peddy output

You could run it as follows on the bash command line:

```{bash, eval=F}
Rscript ~/GEMINI_db_to_SeeGEM.R Family001 ~/See_GEM_Family001.html ~/peddy_output/YOUR_PEDDY_PREFIX
```

If you open up the script in Rstudio (or whatever IDE you prefer), you will
see that the script creates a list object `r GEMINI_list <- list()` then runs
a series of GEMINI queries with the \code{\link{gemini_test_wrapper}} and
\code{\link{gemini_query_wrapper}}. These are fairly lightweight wrappers
and they only do three things to the [GEMINI](http://gemini.readthedocs.io) data:

1. Import the data with the data.table fread function
2. Coerce the `chrom` column to character to avoid possible 1,2,...X,Y issues
3. Add a new column `test` which labels what kind of [GEMINI](http://gemini.readthedocs.io)
query/test was run

If you have your own functioning python/bash scripts creating GEMINI queries 
already, you probably can simply import the data into R as follows:

```{r, eval = F}
library(SeeGEM)
your_gemini_data <- fread('path_to_your_gemini_output.tsv')
your_gemini_data$test <- 'WHAT TEST YOU RAN'
your_gemini_data$chrom <- as.character(your_gemini_data$chrom) # coerce to character
```

Then you can use `your_gemini_data` in the \code{\link{knit_see_gem}} function
as the `GEMINI_data` like so:

```{r, eval = F}
knit_see_gem(GEMINI_data = your_gemini_data, sample_name = 'Proband 001')
```



