---
title: "SeeGEM Quick Start"
author: "David McGaughey"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    theme: flatly
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

## Quick Start
The SeeGEM package contains the information used to create the 
[demo file](https://cdn.rawgit.com/davemcg/SeeGEM_docs/98d1b0cf/demos/demo.html)

Before you get started with your own data, I suggest you recreate this document
to make sure you have all of the libraries and pandoc installed on your computer.

```{r}
library(SeeGEM)
knit_see_gem()
```

This should create `SeeGEM_document.html` in your base user directory (`~/`)

To see an example of what the [peddy](http://peddy.readthedocs.io/en/latest/) 
integrated report looks like run this:

```{r}
knit_see_gem(skip_stats = 'no')
```

Now it is time to use your own data. You will need the following:

  1. GEMINI installed (e.g. if you go to your shell and type `gemini` it will run (with an error about `too few arguments`)
  2. A GEMINI database

You can use the \code{\link{gemini_test_wrapper}} or \code{\link{gemini_query_wrapper}} functions to call
`gemini` from R and pull the data into the \code{\link{knit_see_gem}} function. 

It is much simpler to use the \code{\link{gemini_test_wrapper}} since it has pre-filled out
sensible default filters (see the documentation). You just need need to feed \code{\link{gemini_test_wrapper}}
the GEMINI database ('2018_06_28__OGVFB_exomes.GATK.PED_master.gemini.db'), the
test you want to run ('autosomal_recessive'), finally the family that you want
to return the results from ('DDL003').

Then give the path and name of the output file and tell \code{\link{knit_see_gem}}
to use the use the no stats template with `skip_stats = 'no'`

```{r, eval = F}
knit_see_gem(GEMINI_data = gemini_test_wrapper('2018_06_28__OGVFB_exomes.GATK.PED_master.gemini.db', 
                                               test = 'autosomal_recessive', 
                                               families = 'DDL003'), 
             output_file='quick_SeeGEM.html', 
             skip_stats = 'yes')
```

Depending on the speed of the GEMINI query, this can create the document in seconds, potentially
making it possible to use SeeGEM in an exploratory manner. 

