---
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
title: '`r params$title`'
output: 
  html_document:
    theme: flatly
  css: datatable_fix.css
params:
  GEMINI_data_frame:
    value: NA
  stats:
    value: NA
  sample_name:
    value: FILL_IN
  title:
    value: SampleReport
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = F,
                      warning = F,
                      message = F)
```

```{r, include = FALSE}
# load in data to be displayed
load(params$GEMINI_data_frame)
document_data <- See_GEM_formatter(GEMINI_data)
```


## `r params$sample_name` {.tabset}
```{r, include = FALSE}
#round off values <1 or >1000

```
### Variation
```{r}

DT::datatable(document_data$GEMINI_data %>% mutate_if(is.numeric, funs(as.numeric(formatC(., format = "e", digits = 2)))), #width=1200, 
              escape = FALSE,
              rownames = F, 
              class='compact', 
              filter='bottom',
              extensions = c('FixedColumns','Buttons','FixedHeader'),
              options = list(columnDefs=list(list(targets=document_data$neg_core_index-1, visible = FALSE)),
                             pageLength = 15,
                             fixedHeader = TRUE,
                             lengthMenu = list(c(5, 15, 30, 60, 100, -1), list('5', '15', '30', '60', '100', 'All')),
                             dom = 'Bfrtip',
                             buttons = list(list(extend='pageLength'),
                                            list(extend='colvis', collectionLayout='four-column'),
                                            list(extend='colvisGroup', text='Core Fields', 
                                                 hide=paste(document_data$neg_core_index-1, collapse = ','), 
                                                 show = paste(document_data$core_index-1, collapse = ',')),
                                            list(extend='colvisGroup', text='Show All', show = ':hidden' )),
                             columnDefs=list(list(targets=c(1), class="dt-left")))) 

```

### Statistics

Yes, this is blank right now.

The plan is to add some bare-bones metrics (e.g. number of SNPs, INDELs, ts/tv) that 
`gemini stats` provides for the sample.

The idea is to provide enough information for the analyst to sound the alarm for 
QC-failing samples. 

Potentially [peddy](http://peddy.readthedocs.io/en/latest/) csv output could be 
re-plotted here. 
```{r}


```

### Info

This report is auto-generated with the [See GEM](https://github.com/davemcg/See_GEM) R package on `r strftime(Sys.time(), format = "%B %d, %Y")`

The analyst for this report populated the information in this dynamic documents with a variety of GEMINI queries. 

**FAQ**:

* What does it mean if a variant is marked in red (CURRENTLY NOT IMPLEMENTED)?
* This means that the variant has an impact severity of ['HIGH'](http://gemini.readthedocs.io/en/latest/content/database_schema.html#details-of-the-impact-and-impact-severity-columns) **or** is marked as pathogenic in ClinVar **and** has a population allele frequency less than 10%. 

**WARNINGS/LIMITATIONS** 


