---
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
title: '`r params$title`'
output: 
  html_document:
    theme: flatly
params:
  GEMINI_data_frame:
    value: NA
  peddy_path_prefix:
    value: NA
  peddy_id:
    value: NA
  sample_name:
    value: FILL_IN
  title:
    value: SampleReport
  table_width:
    value: 1500
---

```{r Set parameter loading, include = FALSE}
opts_chunk$set(echo = F,
               warning = F,
               message = F)
```

<style type="text/css">
.main-container {
max-width: `r params$table_width`px; !important;
margin-left: auto;
margin-right: auto;
}
</style>

```{r Load and format GEMINI data, include = FALSE}
# if data given as character, assume it's a path to an Rdata file
if (is.character(params$GEMINI_data_frame)){
  gdf <- load(params$GEMINI_data_frame)
  GEMINI_data <- get(gdf)
  rm(gdf)
}
document_data <- See_GEM_formatter(GEMINI_data)
```

# `r params$sample_name` {.tabset}

## GEMINI Variation
```{r Print GEMINI DataTable}
DT::datatable(document_data$GEMINI_data, 
              width = params$table_width, 
              escape = FALSE,
              rownames = F, 
              class='compact', 
              filter='bottom',
              extensions = c('Buttons','FixedHeader', 'ColReorder'),
              options = list(columnDefs=list(list(targets=document_data$neg_core_index-1, visible = FALSE)),
                             pageLength = 15,
                             scrollX = TRUE,
                             fixedHeader = TRUE,
                             colReorder = TRUE,
                             lengthMenu = list(c(5, 15, 30, 60, 100, -1), list('5', '15', '30', '60', '100', 'All')),
                             dom = 'Bfrtip',
                             buttons = list(list(extend = 'pageLength'),
                                            list(extend = 'colvis', collectionLayout='four-column'),
                                            list(extend = 'colvisGroup', text='Core Fields', 
                                                 hide = paste(document_data$neg_core_index-1, collapse = ','), 
                                                 show = paste(document_data$core_index-1, collapse = ',')),
                                            list(extend = 'colvisGroup', text='Family Genotypes', 
                                                 hide = paste(document_data$neg_genotypes-1, collapse = ','), 
                                                 show = paste(document_data$genotypes-1, collapse = ',')),
                                            list(extend = 'colvisGroup', text='In Silico Fields', 
                                                 hide = paste(document_data$neg_in_silico_index-1, collapse = ','), 
                                                 show = paste(document_data$in_silico_index-1, collapse = ',')),
                                            list(extend='colvisGroup', text='Show All', show = ':hidden' )))) %>% 
  DT::formatStyle(columns = c('Color'), target = 'row', backgroundColor = DT::styleEqual(c(0, 1, 2), c('#ffffff', '#fff0dd', '#ffdddd'))) 


```

## Info

This report is auto-generated with the [See GEM](https://github.com/davemcg/See_GEM) R package on `r strftime(Sys.time(), format = "%B %d, %Y")`

The analyst for this report populated the information in this dynamic documents with a variety of GEMINI queries. 

**FAQ**:

- What does it mean if a variant is marked in red?
- This means that the variant has an impact severity of [HIGH](http://gemini.readthedocs.io/en/latest/content/database_schema.html#details-of-the-impact-and-impact-severity-columns) **or** is marked as pathogenic in ClinVar **and** has a gnomAD population allele frequency less than 1%. 
- Orange?
- [MED](http://gemini.readthedocs.io/en/latest/content/database_schema.html#details-of-the-impact-and-impact-severity-columns) impact severity


**WARNINGS/LIMITATIONS** 

- This document is only a tool to aid identification of causative variant(s)
- The *in silico* consequences (e.g. stop gained, synonymous) are automatically 
calculated, and for a variety of reasons, may not be accurate.
- The causative variants may not be present in this document

